Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-19 paper/paper.tex
Add the conclusion section #59 #55

\section{Conclusions}\label{conclusions}
% Discuss external validity
% Future research: precise border data and RD design

@@

@@

@@

>>>>

\section{Conclusions}\label{conclusions}
% Discuss external validity
% Future research: precise border data and RD design
This study focuses on four unrecognized states in the former Soviet Union. 
Our findings suggest that the impact of non-recognition as sovereign states on economic activities is very limited.

Future research needs to examine whether this conclusion (1) is robust to more rigorous empirical research design and (2) applies to all the other unrecognized states. Constructing the precise data on the boundaries of unrecognized states will allow us to conduct spatial regression discontinuity design to provide credible estimates on the impact of non-recognition.%
\footnote{
	Spatial regression discontinuity design has been employed by Dell (2010), Michalopoulos and Papaioannou (2014), Berger et al.\ (2016), Burgess et al.\ (2018) among others.
}
Extending the analysis to include other unrecognized states outside the former Soviet Union will also help us under what conditions (such as the number of countries recognize them as states) the non-recognition as sovereign states have limited impacts on economic activities.

@@

\bibitem{} Berger, Melissa, Gerlinde Fellner-Rohling, Rupert Sausgruber, and Christian Traxler. 2016. ``Higher Taxes, More Evasion? Evidence from Border Differentials in TV License Fees.'' \textit{Journal of Public Economics}, 135: 74--86.

@@

\bibitem{} Burgess, Robin, Francisco J.M. Costa, and Benjamin Olken. 2018. ``Wilderness Conservation and the Reach of the State: Evidence from National Borders in the Amazon.'' NBER Working Paper, no. 24861.                                                                      

@@

\bibitem{} Dell, Melissa. 2010. ``The Persistent Effects of Peru?s Mining Mita.'' \textit{Econometrica}, 78(6): 1863--1903.
